Fuzzy Extractors for Noisy Sources with More Errors Than Entropy

### 2015-02-10 trunk/constantRate/ConstCompFuzzExt-crypto.tex
did a full pass through all the sections

\iffalse

We construct fuzzy extractors for large classes of such sources by exploiting  their structural properties in addition to their entropy guarantees.  
We show an information-theoretic construction and two computational constructions with additional features.  Our constructions are for the Hamming metric over a nonbinary alphabet.

The information-theoretic construction supports sources in which most symbols contributes fresh entropy. The first computational construction has the additional feature of \emph{reusability}~(Boyen, CCS 2004), allowing multiple correlated

\begin{itemize} \item \textbf{Information-theoretic}  Our first construction supports sources where each symbol contributes fresh entropy and corrects a constant fraction of errors over a super constant size alphabet.

\item \textbf{Computational}
%By adding computational techniques we obtain constructions with additional features.  
Our second construction is also secure when each symbol contributes fresh entropy.  
Additionally, it is a reusable fuzzy extractor~(Boyen, CCS 2004).  A reusable fuzzy extractor allows multiple readings of the source to be enrolled securely.  Our construction is reusable if each individual reading is a supported source.  Previous reusable fuzzy extractors required the correlation between repeated readings to be drawn from a small and unrealistic class.  This construction corrects a sub-constant fraction of errors over a super constant size alphabet.  %Computational techniques allow us to show a very sshows that computational assu computationaprovide requires a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols. It corrects a sub-constant fraction of errors and supports super-constant size alphabets.  In addition, it is first construction of a reusable fuzzy extractor without assumption on the form of errors that occurs between reuse.  This is impossible in the information-theoretic setting for an arbitrary number of reuses~(Boyen, CCS 2004).

Our third construction strengthens the class of supported sources and corrects a constant fraction of errors.  It is secure when individual symbols have high entropy but may be arbitrarily correlated.  This change requires a significantly larger alphabet.

The computational constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.
\end{itemize}
\fi

@@

Our third construction provides information-theoretic, rather than computational, security. It works for \emph{sparse block sources}. These are sources in which a sufficient fraction of the symbols have entropy conditioned on previous blocks. It uses symbol-by-symbol condensers to reduce the alphabet size while preserving most of the entropy, and then applies existing fuzzy extractors to the resulting string.

@@

\begin{table}
\begin{center}
\begin{tabular}{l l l l l}
  & Source Structure & Error Rate  & Techniques\\
\hline
Cons. \ref{cons:sampling} (reusable)  & high-entropy samples & any subconstant &  Sample-then-obfuscate \\
Cons. \ref{cons:first construction}  & sparse high-entropy  marginals & constant &  Error-correct-and-obfuscate\\
Cons. \ref{cons:info theoretic} (info-theoretic)   & sparse block source  & constant & Condense-then-fuzzy-extract\\
\hline\end{tabular}
\end{center}
%end centering
\caption{Summary of new constructions. \consref{cons:sampling} supports the widest class of sources.  The sources supported by the other sources are subsets of high-entropy samples.  \consref{cons:first construction} and \consref{cons:info theoretic} support incomparable classes of sources.}
\label{tab:upper bounds}
\end{table}

@@

%In this work we restrict the distribution of the original reading $w$ and allow $w'$ to be an arbitrary point within distance $t$.  An alternative approach is to restrict the set of $w'$ where $\gen$ produces the correct key. \lnote{move this somewhere that makes more sense, probably above where we talk about a ball around a $w'$ and the obvious impossibility}%  A meaningful restriction of correctable errors is an open problem. 
%\fi
\paragraph{Organization }
The remainder of this paper is organized as follows: we cover notation and fuzzy extractors in \secref{sec:preliminaries}.  We present our information-theoretic construction in \secref{sec:info theory cons} and our two computational constructions in Sections \ref{sec:sampling} and \ref{sec:cor construction}.

@@

\paragraph{Sources with High-Entropy Samples}
Let the source $W=W_1, \dots, W_\gamma$ consist of strings of length $\gamma$ over some arbitrary alphabet $\mathcal{Z}$. For some parameters $\eta, \subsetEntropy$, we say that the source $W$ is a source with  \emph{$(\eta, \subsetEntropy)$-high-entropy samples} if $\Hav(W_{j_1}, \dots, W_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy$ for uniformly random distinct $1< j_1, \dots, j_\eta \le \gamma$. This property can hold, for example, if the symbols $W_i$ are $\eta$-wise independent, and each has entropy at least $\subsetEntropy/\eta$. However, that's not the only way for the property to hold: for example, we can allow sources in which some symbols have little entropy or depend on other symbols, by simply choosing a larger $\eta$ to compensate.

A distribution obtained by applying short-output condensers multiple times to a single sample from a high-entropy source (e.g., via random projections) will have this property, because the outputs of the condensers will be contain fresh entropy as long as the total amount of entropy in the source is not exceeded
(by a simple conditional entropy argument---each subsequent element in the sequence $w_{j_1}, \dots, w_{j_\eta}$ will extract fresh entropy as long as fresh entropy remains conditioned on the previous elements).

\paragraph{The Construction}
The construction first chooses a random $r$ to be used as the output of the fuzzy extractor. It then samples a random subset of symbols $v_1=w_{j_1},..., w_{j_\eta}$ and creates a digital locker that hides $r$ using $v_1$ (We present and analyze the construction with uniformly random subsets; however, if necessary, it is possible to substantially decrease the required public randomness and the length of $p$ by using more sophisticated samplers. See~\cite{goldreich2011sample} for an introduction to samplers.) This process is repeated to produce $\ell$ digital lockers all containing $r$,  each unlockable with $v_1,..., v_\ell$, respectively. The use of the composable digital lockers allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$.  Composability also allows reusability.

\begin{construction}[Sample-then-Obfuscate]
\label{cons:sampling}
Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source with $(\eta, \subsetEntropy)$-high-entropy samples, where each $W_j$ is over $\mathcal{Z}$.  Let $\ell$ be a parameter, to be determined later. 
Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for the family of digital lockers with $\kappa$-bit outputs. Define $\gen, \rep$ as:

@@

\begin{theorem}
\label{thm:sampling}
Let $n$ be a security parameter, $\mathcal{Z}$ be an alphabet, and $\gamma, \subsetEntropy$, and $t$ be functions of $n$, as follows.  Let $\mathcal{W}$ be a family of sources over $\mathcal{Z}^\gamma$ with $(\eta, \subsetEntropy)$ high-entropy samples for $\subsetEntropy = \omega(\log n)$. Let $t$ be such that $\left(1-\frac{t}{\gamma-\eta}\right)^\eta>1/p(n)$ for some positive polynomial $p$. Then it there exists $\ell = \poly(n)$ such that for any
$s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $\left (\epsilon_{sec}, s_{sec}\right)$-hard with negligible error.
\end{theorem}

@@

\paragraph{Any sublinear error-rate can be supported if most symbols in a sample contribute entropy.}
The requirement on $t$ can be expressed as $\eta \log  \left(1-\frac{t }{\gamma-\eta}\right) = O (\log n)$. Using $\ln (1+x)\approx x$ and relying on $O$ to absorb any 
constant factor involved in this approximation and the switch from $\ln$ to $\log$, we get $\eta \frac{t }{\gamma-\eta} = O(\log n)$. If $t$ is sublinear in $\gamma$
 (and $\eta$ is no more than a constant fraction of $\gamma$), then $t/(\gamma-\eta)$ is subconstant, and therefore it is possible to satisfy this requirement on $t$ while simultaneously maintaining $\eta = \omega (\log n)$, which implies $\subsetEntropy = \omega(\log n)$ as long as most symbols in a sample of size $\eta$ contribute a constant amount of entropy each.

@@

\iffalse 
\subsection{Security of \consref{cons:sampling}}
\label{ssec:sec cons sampling}
In this section we outline security of \consref{cons:sampling}.  A proof of security appears in \apref{sec:analysis sampling}.
With overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.   Once each of the $V_1,..., V_\ell$ have high entropy the obfuscations are unlikely to return a value other than $\perp$ to an adversary.
% forms a block-unguessable distribution.  Then security essentially follows from the security of \consref{cons:first construction}. %follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).
%Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.  %By the same argument of Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.
We begin by showing that each $V_i$ is statistically close to a high entropy distribution.   Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda=\lambda_1 \dots \lambda_\ell$
be some particular outcome.

\begin{lemma}
\label{lem:sampling works}
Let all variables be as in \thref{thm:sampling}.
There exists $\epsilon_{sam} = O(e^{-\eta}) = \ngl(n)$ and $\alpha' = \alpha\eta(\gamma-\beta-\eta)/\gamma = \omega(\log n)$ such that for each $i$,
\[
\Pr_{\lambda\leftarrow \Lambda}[\Hoo(V_i | \Lambda= \lambda) \geq \alpha'] \geq 1- \epsilon_{sam}.
\]
\end{lemma}

\noindent
We can then argue that all $V_i$ simultaneously have individual entropy with good probability~(by union bound):
\begin{corollary}
\label{cor:samp sec}
 Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works}, and all the other variables be as in \thref{thm:sampling}.  Then $\Pr_{\lambda\leftarrow \Lambda}[\forall i, \Hoo(V_i | \Lambda = \lambda)  \ge \alpha'] \geq 1-\ell\epsilon_{sam}$.
%[V_i(V, \Lambda)$ is $(\ell\epsilon_{sam})$-close to a distribution $(V', U_{\ell\times r_{sam}})$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
\end{corollary}
%\begin{proof}
%Union bound over the probability in \lemref{lem:sampling works}.
%%Hybrid argument over the statistical distance in \lemref{lem:sampling works}.
%\end{proof}

Once all $V_i$ all simultaneously have good entropy, the adversary only sees $\perp$ as an output from the obfuscations~(with overwhelming probability).  If the adversary only sees $\perp$ from the obfuscations, they have no information about the key.

\begin{lemma}[Proof in \apref{sec:analysis sampling}]
\label{lem:samp unguess}
Let all the variables be as in \thref{thm:sampling}.
For every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_{\kappa}, P))< \epsilon_{sec}$.
\end{lemma}

\subsection{Correctness of \consref{cons:sampling}}
\label{sec:correct sampling}
We encode the entire key in each obfuscation.  For correctness, at least one of the repeated readings must be correct with overwhelming probability.  Let $V_i$ represent one of the initial readings and $V_i'$ represent a repeated reading.  For showing correctness we must show that $\Pr[\forall i, V_i \neq V_i'] < \ngl(n)$.

\begin{lemma}[Proof in \apref{sec:analysis sampling}]
\label{lem:sampling errors}
Let all the variables be as in \thref{thm:sampling}.
 Then $\Pr[\forall i, v_i\neq v_i'] < \ngl(n)$, where the probability is over the coins of $\gen$.
\end{lemma}
\fi

\subsection{Reusability of \consref{cons:sampling}}
The reusability of \consref{cons:sampling} follows from the security of the VGB obfuscator with auxiliary input. Consider any $q = \poly(n)$ number of reuses.  For each fixed $i\in \{1,..., q\}$, we can treat the keys $r_1,\dots, r_{i-1}, r_{i+1}, \dots, r_q$ and the strings $p_1, \dots, p_q$ as auxiliary input to the obfuscation adversary. The result follows by simulatability of this adversary, using the same argument as the proof of Theorem~\label{thm:sampling} in \apref{sec:analysis sampling} (note that the simulator in the definition of composable obfuscation is required to function for arbitrary circuits in the family even if the choice of these circuits depends on the previous obfuscations, which allows reading $w_i$ to be chosen depending on public values $p_1,..., p_{i-1}$).

  Thus, given sufficiently strong reusability we achieve the following result:

@@

\iffalse
\subsection{More errors than entropy?}
In this section, we show when \consref{cons:sampling} supports partial block sources with more errors than entropy.  The structure of the partial block source implies that $\Hoo(W) \ge \alpha (\gamma-\beta ) = \Theta(\gamma)$.  We assume that $\Hoo(W) = \Theta(\gamma)$.  We are able to correct $o(\gamma)$ errors.
This yields:
\[
\text{\# Errors} - \text{Entropy} =  \log |B_t| -\Hoo(W) \ge t \log |\mathcal{Z}| - \Theta(\gamma)= o(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)
\]
That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with more errors than entropy.

\textbf{Notes:} \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, the required entropy is greater than the number of corrected error patterns.  However, \consref{cons:sampling} is reusability for an arbitrary size alphabet.

In the analysis of \consref{cons:sampling} we restricted our attention to partial block sources, to allow for an easy comparison with \consref{cons:info theoretic}.  However,  in fact \consref{cons:sampling}  is secure for any source where sampling produces a high entropy string~(entropy $\omega(\log n)$) with overwhelming probability. For example, it is secure for sources with symbols that are $\omega(\log n)/\log |\mathcal{Z}|$-wise independent.

\fi

\section{Construction for Sources with Sparse High-Entropy Marginals}
\label{sec:cor construction}
\lnote{stopped here; also need to reorder appendices}
In the previous two sections, we presented constructions that supported restricted classes of distributions with more errors than entropy.  Unfortunately, both Constructions~\ref{cons:info theoretic} and \ref{cons:sampling} required each symbol to contribute ``fresh'' entropy.  In this section, we present a computational construction that allows for correlation between symbols while still supporting more errors than entropy and correcting a constant fraction of errors.
This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.  Instead of having large parts of the string $w$ unlock $r$, we have individual symbols unlock bits of the output.

@@

\consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $W_j$.  By the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function. Therefore, our construction is secure as long as enough blocks are unpredictable even after adaptive queries to equality oracles for individual symbols. This restriction on the distribution is captured in the following definition.

\begin{definition}
\label{def:block guessable}
Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(j, w_j')=
\begin{cases}
1 & w_j = w_j'\\
0 & \text{otherwise}.
\end{cases}
\]
A source $W = W_1| ... |W_\gamma$ is a $(q, \alpha, \beta)$-\emph{unguessable block source} if there exists a set $J\subset\{1,..., \gamma\}$ of size at least $\gamma -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
\[
\forall j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}

We show some examples of unguessable block sources in \apref{sec:characterize}.  In particular, any source $W$ where for all $j$, $\Hoo(W_j) \geq \omega(\log n)$~(but all blocks may arbitrarily correlated) is an unguessable block source~(\clref{cl:all blocks entropy}).

Unfortunately, \consref{cons:first construction} is not a computational fuzzy extractor.  The codewords $c$ are not uniformly distributed and it is possible to learn some bits of $c$~(for the symbols of $W$ without much entropy).  However, we can show that $c$ looks like it has entropy.  We use the notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
\label{def:hill ent}
Let $(W, S)$ be a pair of random variables.  $W$ has
\emph{HILL entropy} at least $k$ conditioned on $S$,
denoted $H^{\hill}_{\epsilon_{sec}, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon_{sec}$.
\end{definition}
We now define a weaker object that outputs computational entropy~(instead of a pseudorandom key).  We call this object a computational fuzzy conductor.  It is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
\begin{definition}
\label{def:comp fuzzy cond}
A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
\begin{itemize}
\item for any distribution $W\in \mathcal{W}$, the string $r$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon_{sec}, s_{sec}}(R |P)\geq \tilde{m}$.
\end{itemize}
\end{definition}
Computational fuzzy conductors can be converted to computational fuzzy extractors using standard techniques~(see \apref{sec:further defs}).
The following theorem states the construction is a computational fuzzy conductor~(proof in \apref{sec:construction analysis}).
\begin{theorem}
\label{thm:main thm first cons}
Let $n$ be a security parameter. Let $\mathcal{Z}$ be an alphabet where $|\mathcal{Z}| \ge 2^{ \omega(\log(n))}$.
Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block sources over $\mathcal{Z}^\gamma$, for any $q = \poly(n)$.  Furthermore, let $C$ be a $(t, \delta_{code})$-Z code over $\mathcal{Z}^\gamma$.  Let $\mathcal{O}$ be an $\gamma$-composable VGB obfuscator for point functions with auxiliary inputs. Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec}=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \gamma/|\mathcal{Z}|$.
\end{theorem}

\subsection{More errors than entropy?}
\label{sec:discussion}
In this section, we show that \consref{cons:first construction} can support distributions with more errors than entropy.
We first calculate the size of the Hamming ball.
\[
\log |B_t| = \log \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i> \log {\gamma \choose t} (|\mathcal{Z}|-1)^t =\Theta(t\log |\mathcal{Z}|) + \log {\gamma\choose t}
\]
The simplest type of unguessable block source is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).  For this type of source the entropy is $\Hoo(W) = \gamma\omega(\log n)$.  This yields:
\[
\text{\# errors} - \text{entropy} = \log |B_t| -  \Hoo(W)  >\left( \Theta(t\log |\mathcal{Z}|) + \log {\gamma \choose t}\right) -  \gamma \omega(\log n) .
\]
When $t =\Theta(\gamma)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then the construction supports more errors than entropy. Furthermore, the output entropy is $H_0(C) -\beta$~(if $C$ is a constant rate code, this is $\Theta(\gamma)$).

@@

\section{Information-Theoretic Construction for Sparse Block Sources}
\label{sec:info theory cons}
In this section we show an information-theoretic fuzzy extractor that supports more errors than entropy for sparse block sources.
%Information-theoretic fuzzy conductors can be converted to fuzzy extractors using a randomness extractor~(using the information-theoretic analogue of \lemref{lem:cond and cext}).
The construction first condenses entropy from each block of the source and then applies a different fuzzy extractor to the condensed blocks. We'll denote the fuzzy extractor on the smaller alphabet as $(\gen', \rep')$.  A condenser is like a randomness extractor but the output is allowed to be slightly entropy deficient.  Condensers are known with smaller entropy loss than possible for randomness extractors~(e.g.~\cite{dodis2014key}).
\begin{definition}
\label{def:conductor}
A function $\cond : \mathcal{Z}\times \zo^d\rightarrow \mathcal{Y}$ is a $(m, \tilde{m}, \epsilon)$-randomness condenser if whenever $\Hoo(W)\ge m$, then there exists a distribution $Y$ with $\Hoo(Y)\ge \tilde{m}$ and $(\cond(W, seed), seed) \approx_\epsilon (Y, seed)$.
\end{definition}

>>>>

@@

Our third construction provides information-theoretic, rather than computational, security. It works for \emph{sparse block sources}. These are sources in which a sufficient fraction of the symbols have entropy conditioned on previous symbols. It uses symbol-by-symbol condensers to reduce the alphabet size while preserving most of the entropy, and then applies existing fuzzy extractors to the resulting string.

@@

\begin{table}
\begin{center}
\begin{tabular}{l l l l l}
  & Source Structure & Error Rate  & Techniques\\
\hline
Cons. \ref{cons:sampling} (reusable)  & high-entropy samples & any subconstant &  Sample-then-obfuscate \\
Cons. \ref{cons:first construction}  & sparse high-entropy  marginals & constant &  Error-correct-and-obfuscate\\
Cons. \ref{cons:info theoretic} (info-theoretic)   & sparse block source  & constant & Condense-then-fuzzy-extract\\
\hline\end{tabular}
\end{center}
%end centering
\caption{Summary of new constructions. \consref{cons:sampling} supports the widest class of sources, including sources supported by the other two constructions, but tolerates fewer errors than the other two constructions.  \consref{cons:first construction} and \consref{cons:info theoretic} support incomparable classes of sources.}
\label{tab:upper bounds}
\end{table}

@@

%In this work we restrict the distribution of the original reading $w$ and allow $w'$ to be an arbitrary point within distance $t$.  An alternative approach is to restrict the set of $w'$ where $\gen$ produces the correct key. \lnote{move this somewhere that makes more sense, probably above where we talk about a ball around a $w'$ and the obvious impossibility}%  A meaningful restriction of correctable errors is an open problem. 
%\fi

@@

\paragraph{Sources with High-Entropy Samples}
Let the source $W=W_1, \dots, W_\gamma$ consist of strings of length $\gamma$ over some arbitrary alphabet $\mathcal{Z}$. For some parameters $\eta, \subsetEntropy$, we say that the source $W$ is a source with  \emph{$\subsetEntropy$-entropy $\eta$-samples} if $\Hav(W_{j_1}, \dots, W_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy$ for uniformly random distinct $1< j_1, \dots, j_\eta \le \gamma$. This property can hold, for example, if the symbols $W_i$ are $\eta$-wise independent, and each has entropy at least $\subsetEntropy/\eta$. However, that's not the only way for the property to hold: for example, we can allow sources in which some symbols have little entropy or depend on other symbols, by simply choosing a larger $\eta$ to compensate.

Such sources $W$ can arise naturally as a result of signal processing and discretization. For example, suppose we start with a high-entropy reading $x$ of some physical source, and obtain each symbol $w_i$ by applying a short-output condenser (e.g., a random projection followed by discretization) to $x$. 
Each subsequent element in the sequence $w_{j_1}, \dots, w_{j_\eta}$ will extract fresh entropy as long as there remains entropy in $x$ conditioned on the previous elements (by a simple conditional entropy argument).

\paragraph{The Sample-then-Obfuscate Construction}
The construction first chooses a random $r$ to be used as the output of the fuzzy extractor. It then samples a random subset of symbols $v_1=w_{j_1},..., w_{j_\eta}$ and creates a digital locker that hides $r$ using $v_1$ (We present and analyze the construction with uniformly random subsets; however, if necessary, it is possible to substantially decrease the required public randomness and the length of $p$ by using more sophisticated samplers. See~\cite{goldreich2011sample} for an introduction to samplers.) This process is repeated to produce some number $\ell$ of digital lockers all containing $r$,  each unlockable with $v_1,..., v_\ell$, respectively. The use of the composable digital lockers allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$.  Composability also allows reusability.

\begin{construction}[Sample-then-Obfuscate]
\label{cons:sampling}
Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source with $\subsetEntropy$-entropy $\eta$-samples, where each $W_j$ is over $\mathcal{Z}$.  Let $\ell$ be a parameter, to be determined later. 
Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for the family of digital lockers with $\kappa$-bit outputs. Define $\gen, \rep$ as:

@@

\begin{theorem}
\label{thm:sampling}
Let $n$ be a security parameter, $\mathcal{Z}$ be a constant-size alphabet, and $\gamma, \subsetEntropy$, and $t$ be functions of $n$, as follows.  Let $\mathcal{W}$ be a family of sources over $\mathcal{Z}^\gamma$ with $\alpha$-entropy $\eta$-samples for $\subsetEntropy = \omega(\log n)$. Let $t$ be such that $\left(1-\frac{t}{\gamma-\eta}\right)^\eta>1/p(n)$ for some positive polynomial $p$. Then there exists $\ell = \poly(n)$ such that for any
$s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $\left (\epsilon_{sec}, s_{sec}\right)$-hard with negligible error.
\end{theorem}

@@

\paragraph{Any sublinear error-rate can be supported if most symbols in a sample contribute entropy.}
The requirement on $t$ can be expressed (by taking the negative logarithm of both sides) as $\eta \log  \left(1-\frac{t }{\gamma-\eta}\right) = O (\log n)$. Using $\ln (1+x)\approx x$ and relying on $O$ to absorb any 
constant factor involved in this approximation and the switch from $\ln$ to $\log$, we get $\eta \frac{t }{\gamma-\eta} = O(\log n)$. If $t$ is sublinear in $\gamma$
 (and $\eta$ is no more than a constant fraction of $\gamma$), then $t/(\gamma-\eta)$ is subconstant, and therefore it is possible to satisfy this requirement on $t$ while simultaneously maintaining $\eta = \omega (\log n)$, which implies $\subsetEntropy = \omega(\log n)$ as long as most symbols in a sample of size $\eta$ contribute a constant amount of entropy each.

@@

\subsection{Reusability of \consref{cons:sampling}}
The reusability of \consref{cons:sampling} follows from the security of the VGB obfuscator with auxiliary input. Consider any $q = \poly(n)$ number of reuses.  For each fixed $i\in \{1,..., q\}$, we can treat the keys $r_1,\dots, r_{i-1}, r_{i+1}, \dots, r_q$ and the strings $p_1, \dots, p_q$ as auxiliary input to the obfuscation adversary. The result follows by simulatability of this adversary, using the same argument as the proof of Theorem~\ref{thm:sampling} in \apref{sec:analysis sampling}. Note that the simulator in the definition of composable obfuscation is required to function for arbitrary circuits in the family even if the choice of these circuits depends on the previous obfuscations, which allows the $i$th reading of $w$ to be chosen depending on public values $p_1,..., p_{i-1}$, as required by definition of reusability.

  Thus we achieve the following result:

@@

\section{Construction for Sources with Sparse High-Entropy Marginals}
\label{sec:cor construction}
In this section, we consider an alternative construction that is particularly well suited to sources over large alphabets. It requires enough symbols individually to contain sufficient entropy, but does not require independence of symbols, or even ``fresh'' entropy from them. Unlike the previous construction, it tolerates a linear fraction of errors. However, it cannot work for small alphabets, and is not reusable.

\paragraph{Sources with Sparse High-Entropy Marginals} This construction works for distributions $W=W_1, ... ,W_\gamma$ over $\mathcal{Z}^\gamma $ in which enough symbols $W_j$ are unpredictable even after adaptive queries to equality oracles for other symbols. This quality of a distribution is captured in the following definition.

\begin{definition}
\label{def:block guessable}
Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(j, w_j')=
\begin{cases}
1 & w_j = w_j'\\
0 & \text{otherwise}.
\end{cases}
\]
A source $W = W_1, ... ,W_\gamma$ has $\beta$-sparse $\alpha$-entropy $q$-marginals if there exists a set $J\subset\{1,..., \gamma\}$ of size at least $\gamma -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
\[
\forall j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}

We show some examples of such sources in \apref{sec:characterize}.  In particular, any source $W$ where for all $j$, $\Hoo(W_j) \geq \omega(\log n)$~(but all symbols may arbitrarily correlated) is a source with sparse high-entropy marginals~(\clref{cl:all blocks entropy}).

\paragraph{The Error-Correct-and-Obfuscate Construction}
This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.  Instead of having large parts of the string $w$ unlock $r$, we have individual symbols unlock bits of the output.

@@

As presented, \consref{cons:first construction} is not yet a computational fuzzy extractor.  The codewords $c$ are not uniformly distributed and it is possible to learn some bits of $c$~(for the symbols of $W$ without much entropy).  However, we can show that $c$ looks like it has entropy to a computationally bounded adversary who knows $p$. Applying a randomness extractor with outputs over $\zo^\kappa$ (technically, an average-case computational randomness extractor) to $c$, and adding the extractor seed to $p$, will give us the desired fuzzy extractor. See \apref{sec:further defs} for the formal details.

\consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $W_j$.  By the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function. Therefore, our construction is secure as long as enough symbols are unpredictable even after adaptive queries to equality oracles for individual symbols, which is exactly the property satisfied by sources with sparse high-entropy marginals.

The following theorem formalizes this intuition~(proof in \apref{sec:construction analysis}).
\begin{theorem}
\label{thm:main thm first cons}
Let $n$ be a security parameter. Let $\mathcal{Z}$ be an alphabet where $|\mathcal{Z}| \ge 2^{ \omega(\log(n))}$.
Let $\mathcal{W}$ be a family of sources with $\beta$-sparse $\alpha=\omega(\log n)$-entropy $q$-marginals over $\mathcal{Z}^\gamma$, for any $q = \poly(n)$.  Furthermore, let $C$ be a $(t, \delta_{code})$-Z code over $\mathcal{Z}^\gamma$.  Let $\mathcal{O}$ be an $\gamma$-composable VGB obfuscator for point functions with auxiliary inputs. Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec}=\ngl(n)$ such that \consref{cons:first construction}, followed by a $\kappa$-bit randomness extractor, is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \gamma/|\mathcal{Z}|$.
\end{theorem}

\paragraph{More Errors than Entropy?}
\label{sec:discussion}
In this section, we show that \consref{cons:first construction} can support distributions with more errors than entropy.
We first calculate the size of the Hamming ball.
\[
\log |B_t| = \log \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i> \log {\gamma \choose t} (|\mathcal{Z}|-1)^t =\Theta(t\log |\mathcal{Z}|) + \log {\gamma\choose t}
\]
The simplest type of a source with high-entropy marginals is where each symbol is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).  For this type of source the entropy is $\Hoo(W) = \gamma\omega(\log n)$.  This yields:
\[
\text{\# errors} - \text{entropy} = \log |B_t| -  \Hoo(W)  >\left( \Theta(t\log |\mathcal{Z}|) + \log {\gamma \choose t}\right) -  \gamma \omega(\log n) .
\]
When $t =\Theta(\gamma)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then the construction supports more errors than entropy. Furthermore, the output entropy is $H_0(C) -\beta$~(if $C$ is a constant rate code, this is $\Theta(\gamma)$).

@@

\section{Information-Theoretic Construction for Sparse Block Sources}
\label{sec:info theory cons}
The construction in this section has information-theoretic security, in contrast to only computational security of the previous two constructions. It requires less entropy from each symbol than the previous construction; however, it places more stringent independence requirements on the symbols. It tolerates a linear number of errors.

\paragraph{Sparse Block Sources}
This construction works for sources $W=W_1, ... ,W_\gamma$ over $\mathcal{Z}^\gamma $ in which enough symbols $W_j$ contribute fresh entropy conditioned on previous symbols.  We call this such sources \emph{sparse block sources}, weakening the notion of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), which require every symbol to contribute fresh entropy.

\begin{definition}
\label{def:partial source}
A distribution $W = W_1,..., W_\gamma$ is an $(\alpha, \beta)$-sparse block source if there exists a set of indices $J$ where $|J| \geq \gamma - \beta$ such that the following holds:
\[
\forall j\in J, \forall w_1,..., w_{j-1} \in W_1,..., W_{j-1}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
\]
\end{definition}
The choice of conditioning on the past is arbitrary: a more general sufficient condition is that there exists some ordering of indices where most items have entropy conditioned on all previous items in this ordering~(for example, is possible to consider a sparse reverse block source~\cite{vadhan2003constructing}).
